MLExplain

### 2018-05-24 paper.tex
Ajouté un paragraphe sur les constructeurs de type

At first glance, JSExplain seems tightly linked to JavaScript. However, the
architecture of the project actually lets us completely replace the interpreter
with one for a different language.

@@

% Difference entre les constructeurs, raison principale de la traduction à la
% main

@@

Error management could not be done using exceptions. This is why we used monadic
computation. A monad is a data structure representing an action within a
context. A monad typically take the form of a type constructor. It provides the
following functions:

@@

\begin{figure}[b]
  \begin{verbatim}
let bind_option opt f = match opt with
| Some value -> f value
| None -> None
  \end{verbatim}

>>>>

At first glance, JSExplain seems tightly linked to JavaScript. However, the
architecture of the project actually lets us completely replace the interpreter
with one for a different language. Our main task was to create a new OCaml
interpreter that could be integrated into the rest of the application. Then, we
noticed that the web application itself needed some changes -- for instance to
pretty print values.

@@

% TODO: Alan, si tu as une idée pour raccourcir ou découper cette phrase
The main reason why both AST representations are not compatible and require an
explicit hand-made serialization into JavaScript is how the compilers compile
OCaml type constructors. Our compiler creates a JavaScript object from the type
and treats constructors as methods building themselves the value. This value is
a simple JavaScript object. \emph{js\_of\_ocaml}, on the other hand, uses its
own internal representation of OCaml value that we cannot use directly.

@@

Error management could not be done using exceptions. This is why we used monadic
computation. A monad is a data structure representing an action within a
context. A monad typically take the form of an algebraic type. It provides the
following functions:

@@

\begin{figure}[hb]
  \begin{verbatim}
let bind_option opt f = match opt with
| Some value -> f value
| None -> None
  \end{verbatim}
